Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-01-29 main.tex
update window figureds

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 134--135$^\circ$ distance and 1375--1,376~s time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density_Z}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
   The maximum window count is 7,542.
   }
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
   The maximum window count is 7,208.
   Only SH travetime branches are labeled.}
  \label{fig:window_density_T}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_Z.pdf}
  \caption{Time-distance plot for vertical component 17--40~s body waves showing a measurement window density map.
  A total of 4,363,719 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 9,931 in the 85--86$^\circ$ distance and 1,375--1,376~sec time bin.
  Major traveltime branches are labeled. Note that the plot contains data from events with a wide variety of depths, so the branches are for identification purposes only.
  }
  \label{fig:window_density_Z}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_R.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for radial component 17--40~s body waves.
   A total of 2,868,252 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
  The maximum window count is 7,542 in the 86--87$^\circ$ distance and 1,378--1,379~sec time bin.
   }
  \label{fig:window_density_R}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{figures/window_colorbar_linear_T.pdf}
  \caption{Same as Fig.~\ref{fig:window_density_Z}, except for transverse component 17--40~s body waves.
   A total of 2,151,856 time windows were discretized into 1~degree epicentral distance and 1~s time bins.
   The maximum window count is 7,208 in the 89--90$^\circ$ distance and 1,398--1,399~sec time bin.
   Only SH travetime branches are labeled.}
  \label{fig:window_density_T}
\end{figure}
